\documentclass[a4paper]{book}

% --- FONT AND ENCODING (Core) ---
\usepackage[T1]{fontenc} % Output font encoding
\usepackage{microtype} % Improves typography (spacing, justification)

% --- PAGE LAYOUT AND GEOMETRY ---
\usepackage[left=.7in, right=.7in, top=1.2in, bottom=1in]{geometry}

% --- HEADER AND FOOTER ---
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[LE]{\nouppercase{\leftmark}} % Chapter name on even pages (left)
\fancyhead[RO]{\nouppercase{\rightmark}} % Section name on odd pages (right)
\fancyfoot[C]{\thepage} % Page number in the center of the footer
\renewcommand{\headrulewidth}{0.4pt} % Rule under the header
\renewcommand{\footrulewidth}{0pt} % No rule over the footer
\fancypagestyle{plain}{%
  \fancyhf{}% Clear header/footer for plain pages (e.g., chapter starts)
  \fancyfoot[C]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{0pt}%
}

% --- MATHEMATICS PACKAGES (Base and Standard Symbols) ---
\usepackage{amsmath}
\usepackage{amsfonts} % Loads amssymb implicitly or defines symbols amssymb relies on
\usepackage{amssymb}  % For additional math symbols
\usepackage{amsthm}   % For theorem-like environments if needed

% --- FONT PACKAGES (Text and Math - load after ams packages) ---
\usepackage{newtxtext, newtxmath} % Times-like font for text and math


% --- CUSTOM DERIVATIVE COMMANDS ---
% For first derivative: \dv{y}{x}
\newcommand{\dv}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}

% For second derivative: \ddv{y}{x} (will typeset d^2y / dx^2)
% Note: This assumes the second argument 'x' is a single variable.
% If you need d^2y / d(t^2)^2 (which is unusual), you'd need a different command or pass {{t^2}}
\newcommand{\ddv}[2]{\frac{\mathrm{d}^2 #1}{\mathrm{d} #2^2}}

% For partial derivatives (optional, but good to have if you plan to use them)
% \pdv{f}{x}
\newcommand{\pdv}[2]{\frac{\partial #1}{\partial #2}}
% \pddv{f}{x} for d^2f/dx^2 (partial)
\newcommand{\pddv}[2]{\frac{\partial^2 #1}{\partial #2^2}}
% \pddv{f}{x}{y} for d^2f/(dx dy) (partial)
\newcommand{\pddvxdy}[3]{\frac{\partial^2 #1}{\partial #2 \partial #3}}

% --- MATHEMATICS UTILITIES (Load after font and core math setup) ---
\usepackage{siunitx}  % For SI units
\AtBeginDocument{%
  \RenewCommandCopy\qty\SI % Makes \qty from physics behave like \SI from siunitx for {value}{unit}
}

% --- LISTS AND TABLES ---
\usepackage{multicol} % For multi-column layout
\usepackage{enumitem}
\setlist[enumerate]{itemsep=3pt, topsep=5pt, partopsep=2pt}
\usepackage{booktabs} % For professional-looking tables
\usepackage{cancel}   % For striking out terms in math

% --- GRAPHICS AND DIAGRAMS ---
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning}

% --- TABLE OF CONTENTS AND SECTIONING ---
\usepackage{titlesec}
\usepackage{tocloft}
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftbeforechapskip}{10pt}

% --- HYPERLINKS AND REFERENCING ---
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    citecolor=purple,
    pdftitle={Acing UTME Maths},
    pdfauthor={Ayodeji Adesegun and Chimobi Nwafor},
    bookmarksopen=true,
    bookmarksnumbered=true
}
\usepackage{cleveref} % Load after hyperref

% --- BIBLIOGRAPHY ---
\usepackage{biblatex}
% \addbibresource{your_bibliography_file.bib}

% --- TITLE PAGE ---
\usepackage{titling}

% --- DOCUMENT START ---
\begin{document}

% --- TITLE PAGE ---
\begin{titlingpage}
\centering
\vspace*{\fill}
\Huge\textbf{Acing UTME Maths}\\
\vspace{1cm}
\Large{A Comprehensive Guide with Past Questions and Solutions}\\
\vspace{2cm}
\Large\textbf{By}\\
\vspace{0.5cm}
\Large\textbf{Ayodeji Adesegun and Chimobi Nwafor}\\
\vspace*{\fill}
\Large{\today}\\
\vspace*{\fill}
\end{titlingpage}

% --- FRONTMATTER ---
\begin{frontmatter}
\pagestyle{plain}

\chapter*{Dedication and Acknowledgements}
This work is dedicated to our families, whose unwavering support has been our greatest strength throughout this journey. Their constant encouragement and belief in our abilities have fueled our passion and perseverance in creating this resource.

We would also like to express our sincere gratitude to the following individuals and institutions for their invaluable contributions:
\begin{itemize}
\item Our mentors and teachers, who instilled in us a love for mathematics and equipped us with the knowledge and skills needed to succeed.
\item The examiners and administrators of the UTME, whose dedication to educational standards ensures a fair and effective assessment process.
\item  Our colleagues and friends, who provided feedback and support throughout the development of this book.
\item The wider academic community, whose research and publications have laid the foundation for our understanding of mathematics.
\end{itemize}
We are truly grateful for the collective effort that has made this book possible. We hope that it will be a valuable resource for students preparing for the UTME and beyond.

\section*{A Note on Preparation}
This book was meticulously prepared using the \LaTeX\ document processing system, a powerful tool for typesetting high-quality scientific and mathematical texts. The diagrams herein were crafted using the TikZ package. We extend our thanks to the developers of the \LaTeX\ system and the numerous packages that made this work possible.

\section*{About the Authors}
\begin{description}
\item[\href{https://linkedin.com/in/ayodejiades}{\textbf{Ayodeji Adesegun}}:] He is a teenager. In his spare time, he enjoys solving mathematical problems from various contests not excluding the Olympiads. You can find more about him \href{https://ayodejiades.vercel.app}{here.}
\item[\href{https://linkedin.com/in/jeremaih-nwafor}{\textbf{Chimobi Nwafor}}:] He is a software engineer trainee at INITS.
\end{description}

\clearpage
\tableofcontents
\clearpage

\chapter*{Preface}
Welcome to ``Acing UTME Maths'', a comprehensive guide designed to help you conquer the upcoming UTME Maths exam. This book provides you with a wealth of past questions, detailed solutions, and insightful strategies to enhance your understanding and preparation.

This book is organized into chapters that follow the official UTME Maths syllabus, covering all key topics and subtopics. Each chapter includes a variety of past questions carefully selected to reflect the types and difficulty levels encountered in the actual exam.

In addition to past questions, we have provided detailed solutions that explain the reasoning behind each step and highlight common mistakes to avoid. We encourage you to work through these solutions carefully and utilize them as learning tools to improve your problem-solving skills.

Furthermore, we have incorporated valuable strategies throughout the book, offering tips and techniques to maximize your efficiency and performance on the exam. These strategies will help you manage your time effectively, approach different question types confidently, and overcome any challenges you may encounter.

We are confident that ``Acing UTME Maths'' will be your ultimate companion on your journey to success. By diligently working through the material and utilizing the resources provided, you will gain the knowledge, skills, and confidence needed to achieve your desired score on the UTME Mathematics exam.

Best of luck!

Ayodeji Adesegun and Chimobi Nwafor
\clearpage
\end{frontmatter}

% --- MAINMATTER ---
\mainmatter
\pagestyle{fancy}

% Chapter organization
\include{number}
\include{fraction}
\include{algebra}
\include{indices}
\include{surds}
\include{logarithms}
\include{geometry}
\include{coordinate}
\include{differentiation}
\include{integration}
\include{combinatorics}
\include{probability}
\include{statistics}
\include{things}

% --- BACKMATTER ---
\begin{backmatter}
\pagestyle{plain}

% \printbibliography % If using biblatex
\end{backmatter}

\end{document}